---
title: "Predicting the Risk of Recurrent MI"
subtitle: 'SIBS Hackathon Presentation'
author: "Kevin Krupa, Lucy Liu, Kendall McClellan, Connor McNeill"
institute: "NCSU-Duke Summer Institute in Biostatistics"
date: "July 21, 2022"
output: 
  beamer_presentation: 
    theme: Frankfurt
    keep_tex: yes
#    colortheme: 'beaver'
#    fonttheme: structurebold
    includes:
      in_header: 'header.tex'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r coding for later, include=FALSE}
source('hackathon-exploratory-data-analysis.R',
       local=knitr::knit_global())
```

# Introduction

## Background

- Bullet 1

- Bullet 2

- Bullet 3

## Research Question

\begin{block}{Question 1}
What can we look at either during admission or the hospital stay in patients post-heart attack (myocardial infarction) to predict the risk of having a relapse?
\end{block}

\begin{block}{Question 2}
Which risk prediction model is best at predicting a recurrent heart attack?
\end{block}

## Missing Data

- 7.6% missing values

- Used `mice` library in `R` 

    - Predictive Mean Modeling
    
    - 1700 completed observations instead of 0!

# Descriptive Analysis


## Response Variable Correlation

```{r ResVarCorrPlot, warning=FALSE}
corrplot(res, type='upper', order='hclust',
         tl.col='black', tl.srt=45)
```


# Inferential Analysis

## Model Building

Logistic regression is the basis

- Response variable (recurrent MI) is binary

- Multiple predictors

    - $>100$ covariates to begin
    
    - Several removed from consideration due to missingness
    
    - 

## Model Building

Two methods to select significant predictors:

1. Backwards Elimination using AIC (`stepAIC`)
    
2. Elastic Net Penalized Regression (`glmnet`)

Methods will pick predictors and build model

## Model

$$ REC\_IM = \beta_0 + \beta_1 x_1 $$

\end{subsection}

# Discussion

# Conclusion

##
\begin{block}{}
\begin{center}
\Large{Questions??}
\end{center}
\end{block}