---
title: "SIBS Hackathon Presentation"
author: "Kevin Krupa, Lucy Liu, Kendall McClellan, Connor McNeill"
institute: "NCSU-Duke Summer Institute in Biostatistics"
date: "July 21, 2022"
output: 
  beamer_presentation:
    theme: 'Frankfurt'
#    colortheme: 'beaver'
#    fonttheme: structurebold
    includes:
      in_header: 'header.tex'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r coding for later, include=FALSE}
source('hackathon-exploratory-data-analysis.R',
       local=knitr::knit_global())
```

# Introduction

## Background

- Bullet 1

- Bullet 2

- Bullet 3

## Research Question

<!-- \begin{block}{Research Question} -->
<!-- What can we measure to predict a risk of having another relapse? -->
<!-- \end{block} -->

# Descriptive Analysis

## Response Variable Correlation

```{r ResVarCorrPlot, warning=FALSE}
corrplot(res, type='upper', order='hclust',
         tl.col='black', tl.srt=45)
```


# Inferential Analysis

## Intro
LASSO Logistic Regression Model because
- Reduce number of variables (LASSO)
- Response variable is binary (Logistic Regression)

## Model

$$ REC\_IM = \beta_0 + \beta_1 x_1 $$

# Discussion

# Conclusion

##
\begin{block}{}
\begin{center}
\Large{Questions??}
\end{center}
\end{block}